Mobile Assets in Semantic Digital Twins

### 2023-04-22 paper/main.tex
Add updated Introduction

\section{Introduction}
\subsection{Context}
A digital twin (DT) is a digital representation of some physical system, referred to as a physical twin (PT), that is twinned in near real-time by the DT in order to understand or control the PT. The twinning aims to be bi-directional meaning that the DT both observes the PT and communicates informed decisions back to it \cite{kamburjan_digital_2022}. The DT must continually adapt to correctly reflect its physical twin. This may pose a challenge if the PT contains mobile assets.

The notion of mobile assets refers to movable assets, such as smartphones. The number of smartphone users worldwide is at an all-time high \cite{petroc_taylor_number_2023}. Mobile assets are important resources for a company and can change over time. A company should aim to increase the availability of movable assets \cite{marcheta_development_2022}. In our proposal, we should keep in mind that a smartphone's physical location can change at any time.

\begin{comment}

\end{comment}

\subsection{Motivation}
Given the challenges that exist in managing mobile assets, there is still room for improvement. There exist systems that mainly focus on tracking mobile assets and the accuracy of their physical location \cite{marcheta_development_2022,akram_design_2021}. If we keep the company's assets in mind, such a system could be improved upon by better understanding and controlling asset behaviour.

Furthermore, there is existing research about using building information models (BIM) with standard data formats, such as JSON\footnote{\url{https://www.json.org/json-en.html}} and RDF\footnote{\url{https://www.w3.org/RDF/}} to better define static building infrastructure \cite{pauwels_live_2023}. \citeauthor{pauwels_live_2023} proposes how, and to what extent, such data can be used in robot navigation. Although BIM can be used, by default it has some challenges regarding interoperability \cite{dinis_bim_2022} due to heterogeneous data. In an attempt to formalize data and make it understood by computers, semantic web technologies should be used. Another benefit is reduced costs due to less updates of the BIM by maintainers \cite{hamledari_ifc-based_2018}.
More specifically, we aim to semantically enrich a model of a building to increase interoperability, as well as making a coupled connection between the movable entities and the building model. Whilst keeping it easy to maintain and cheap.

We envision a semantic digital twin based on an asset model that can track many heterogeneous movable entities simultaneously. The DT and asset model will be formalized using semantic web technologies, and the asset model will be dynamic. Automatically reloaded by the system itself, or manually updated by an operator either offline (online version updated from local changes), or directly online in an ontology editor. This way the mobile assets are not only tracked, but the physical system containing them is twinned in near-real time as well. The DT will get positional sensor data from the PT, and then send informed decisions back to the PT. If the DT decides some movable entities are inside a critical area, they will be informed in due time.

\subsection{Problem statement}
From the context of digital twins and an increasing number of smartphone users, as well as the motivation for improving the semantics, we present the following hypothesis:

\begin{itemize}
    \item[H:] We can better handle mobile assets in a semantic digital twin with the use of a dynamic asset model, in which dynamic data (smartphone's physical location) is automatically updated by a server and separated from static data (existing building infrastructure).
\end{itemize}

In addition to this, we present the following research questions which will guide this thesis:
\begin{itemize}
    \item[RQ1:] Can we create a dynamic model of a building that is extensible?
    \item [RQ2:] Can we enable bi-directional data flow between the PT and DT, such that the digital twin gets updated sensor data from a mobile device and sends informed decisions back to it?
    \item [RQ3:] Can we clearly separate dynamic data (smartphone's position) from static data (building infrastructure) in the asset model and in the DT?
\end{itemize}

@@

\subsection{Thesis scope and outline}
The scope of this thesis is to handle an unlimited number of mobile assets in a semantic digital twin based on a dynamic asset model. Figure \ref{fig:components} shows the possible overview of architectural components and the bi-directional data flow between the PT and DT. The digital twin should be developed in Semantic Micro Object Language (SMOL)\footnote{\url{https://smolang.org/}} by using its interpreter \footnote{\url{https://github.com/smolang/SemanticObjects}}.
As noted by \citeauthor{pauwels_live_2023} many physical objects, such as furniture and doors, can be movable entities in a building apart from the robots. We limit ourselves to physical devices in 2D space. Doors will have one state (open). The areas are predefined squares with latitude and longitude ranges assuming the coordinates align. An area's two border corners are expressed as follows:
\begin{enumerate}
    \item $(x_1, y_1)$
    \item $(x_2, y_2)$
\end{enumerate}
Meaning, if we want to check if a smartphone's physical location (point) $(x, y)$ is inside such an area, we can check if the following is true:\newline\newline$(x >= x_1\:AND\: x <= x_2)\:OR\:(x >= x_2\:AND\:x <= x_1)$\newline$AND$\newline$(y >= y_1\:AND\:y <= y_2)\:OR\:(y >= y_2\:AND\:y <= y_1)$\include\newline We also include both directions so maintainers can freely choose border corners for an area. Square areas are easier to compute and scale into larger areas, and we are not focusing on other shapes such as polygons.\newline
Figure \ref{fig:simple_building} shows a simple building with two rooms connected by a wall with a door (open) in it.

@@

The remainder of this thesis is organized as follows:
\begin{itemize}
    \item \hyperref[sec:Background]{Background} describes the background of this thesis.
    \item \hyperref[sec:Analysis]{Analysis and design} investigates the problem statement and research questions. We also look at what a dynamic asset model entails, as well as the separation of static and dynamic data.
    \item \hyperref[sec:Implementation]{Implementation} looks into the implementation of the proposed solution and how the different architectural components outlined in Figure \ref{fig:components} interact. More specifically, how do we close the loop by sending informed decisions back to the PT. 
    \item \hyperref[sec:Evaluation]{Evaluation} evaluates the proposed solution according to the requirements that were set earlier.
    \item \hyperref[sec:Discussion]{Discussion} discusses the discoveries of this thesis and compares them to other existing results and theories, as well as explores the originality of the discoveries.
    \item \hyperref[sec:Conclusion]{Conclusion and further work} concludes this thesis. Mainly we look at the improvements that can be made to the proposed solution and the road ahead.  
\end{itemize}

@@

>>>>

\section{Introduction}
\subsection{Context}
A digital twin (DT) is a digital representation of some physical system, referred to as a physical twin (PT), that is twinned in near real-time by the DT in order to understand or control the PT. The twinning aims to be bi-directional meaning that the DT both observes the PT and communicates informed decisions back to it \cite{kamburjan_digital_2022}. The DT must continually adapt to correctly reflect its physical twin \cite{kamburjan_twinning-by-construction_2022}. This may pose a challenge if the PT contains mobile assets.

The notion of mobile assets refers to movable assets, such as smartphones. The number of smartphone users worldwide is at an all-time high \cite{petroc_taylor_number_2023}. Mobile assets are important resources for a company and can change at any time, and a company should aim to increase their availability \cite{marcheta_development_2022}.

There exist challenges in handling mobile assets. Some systems mainly focus on tracking mobile assets and the accuracy of their physical location \cite{marcheta_development_2022,akram_design_2021}. If we keep the company's assets in mind, such a system could be improved upon by better understanding and controlling asset behaviour. Furthermore, there is existing research about using Building Information Modeling (BIM) with standard data formats, such as JSON\footnote{\url{https://www.json.org/json-en.html}} and RDF\footnote{\url{https://www.w3.org/RDF/}} to better define static building infrastructure \cite{pauwels_live_2023}. \citeauthor{pauwels_live_2023} proposes how, and to what extent, such data can be used in robot navigation. Although BIM can be used, by default it has some challenges regarding interoperability due to heterogeneous data \cite{dinis_bim_2022,godager_concept_2021}. It is stated by \citeauthor{godager_concept_2021} that although BIM could serve as a basis for DTs by providing lots of relevant information, DTs give even more context about the built environment, especially by monitoring assets from near real-time data. Using BIM is also very costly due to frequent updates by maintainers \cite{hamledari_ifc-based_2018}.

\subsection{Motivation}
Given the gap the exists in connecting tracking systems, asset models (i.e. a file that contains an organized description of an asset's composition and properties \cite{kamburjan_twinning-by-construction_2022}) and digital twins, there is still room for improvement. In an attempt to formalize heterogeneous data and make it understood by computers, semantic web technologies should be used. More specifically, we aim to semantically enrich a model of a building to increase interoperability, as well as keeping it inexpensive and easy to maintain.

We envision a semantic digital twin (i.e. a digital twin that processes heterogeneous data from different sources in the domain into generally understandable information \cite{birgit_boss_digital_nodate}) based on an asset model that can track many mobile assets simultaneously. The DT and asset model will be formalized using semantic web technologies, and the asset model will be dynamic. Automatically reloaded by the system itself, or manually updated by an operator either offline (online version updated from local changes), or directly online in an ontology editor. This way the mobile assets are not only tracked, but the physical system containing them is twinned in near-real time as well. The DT will get positional sensor data from the PT, and then send informed decisions back to the PT. If the DT decides some movable entities are inside a critical area, they will be informed in due time.

\subsection{Problem statement}
From the context of digital twins and an increasing number of smartphone users, as well as the motivation for improvement, we present the following hypothesis:

\begin{itemize}
    \item[H:] We can handle mobile assets in a semantic digital twin (DT) with the use of a dynamic asset model of a simple building, in which dynamic data (smartphone's physical location) is automatically updated by a server and separated from static data (existing building infrastructure), and informed decisions are sent back to the PT.
\end{itemize}

In addition to this, we present the following research questions which will guide this thesis:
\begin{itemize}
    \item[RQ1:] Can we create an dynamic asset model of a simple building that is also extensible?
    \item [RQ2:] Can we enable bi-directional data flow between the PT and DT, such that the digital twin gets updated sensor data from mobile devices and sends informed decisions back?
    \item [RQ3:] Can we clearly separate dynamic data (smartphone's position) from static data (building infrastructure) in the asset model and in the DT?
\end{itemize}

@@

\subsection{Thesis scope and outline}
The scope of this thesis is to handle an unlimited number of mobile assets in a semantic digital twin based on a dynamic asset model. Figure \ref{fig:components} shows the possible overview of architectural components and the bi-directional data flow between the PT and DT. The digital twin should be developed in Semantic Micro Object Language (SMOL)\footnote{\url{https://smolang.org/}} by using its interpreter \footnote{\url{https://github.com/smolang/SemanticObjects}}.
As noted by \citeauthor{pauwels_live_2023} many physical objects, such as furniture and doors, can be movable entities in a building apart from the robots. We limit ourselves to physical devices in 2D space. Doors will have one state (open). The areas are predefined squares with latitude and longitude ranges assuming the coordinates align. Square areas are easier to compute and scale into larger areas, and we are not concerned with other shapes such as polygons.\newline
Figure \ref{fig:simple_building} shows a simple building with two rooms connected by a wall with a door (open) in it.

@@

The remainder of this thesis is organized as follows:
\begin{itemize}
    \item \hyperref[sec:Background]{Background} describes the theoretical background of this thesis.
    \item \hyperref[sec:Analysis]{Analysis and design} investigates the problem statement and research questions. We also look at what a dynamic asset model entails, as well as the separation of static and dynamic data.
    \item \hyperref[sec:Implementation]{Implementation} dives into the implementation of the proposed solution and how the different architectural components outlined in Figure \ref{fig:components} interact. More specifically, how do we close the loop by sending informed decisions back to the PT. 
    \item \hyperref[sec:Evaluation]{Evaluation} evaluates the proposed solution according to the requirements that were set earlier.
    \item \hyperref[sec:Discussion]{Discussion} discusses the discoveries of this thesis and compares them to other existing results and theories, as well as explores the originality of the discoveries.
    \item \hyperref[sec:Conclusion]{Conclusion and further work} concludes this thesis. Mainly we look at the improvements that can be made to the proposed solution and what lies ahead.  
\end{itemize}

@@

An area's two border corners are expressed as follows:
\begin{enumerate}
    \item $(x_1, y_1)$
    \item $(x_2, y_2)$
\end{enumerate}
Meaning, if we want to check if a smartphone's physical location (point) $(x, y)$ is inside such an area, we can check if the following is true:\newline\newline$(x >= x_1\:AND\: x <= x_2)\:OR\:(x >= x_2\:AND\:x <= x_1)$\newline$AND$\newline$(y >= y_1\:AND\:y <= y_2)\:OR\:(y >= y_2\:AND\:y <= y_1)$\include\newline We also include both directions so maintainers can freely choose border corners for an area.
